---
title: "The Making of the Corpus for Macro"
output: 
  html_document:
    toc: true
    number_sections: true
    toc_float: true
    code_folding: hide
    df_print: paged
---

```{r, set.seed(2000)}
knitr::opts_chunk$set(cache = T)
```

```{r setup, include=FALSE}
library(knitr)
knitr::opts_knit$set(root.dir = "/projects/data/macro_AA")
library(png)
library(grid)
library(ggnewscale)
library(vite)
library(RMySQL)
library(NetworkToolbox)
library(broom)
library(igraph)
library(data.table)
library(ggplot2)
library(magrittr)
library(tm)
library(tidyr)
library(tidytext)
library('cluster')
library('ggraph')
library('tibble')
library('tidygraph')
library(ggrepel)
library(readr)
library(leiden)
library(ggraph)
library(ggnewscale)
library(remotes)
library(vite)
library("reticulate")
library(reticulate)
library(leiden)
library(tidygraph)
library(rlang)
library(leiden)
library(ggforce)
library(d3Network)
library(scales)
library(RColorBrewer)
require(DescTools)
require(stringr)
color = data.table(
  Leiden1 = 1:500,
  color = brewer.pal(8, name = "Dark2"))
color[Leiden1>8 & Leiden1<=16, color:=brewer.pal(8, name = "Set1")]
color[Leiden1>10, color:="#c2c2c2"]
color[,Leiden1:=sprintf("%02d", Leiden1)]
color[,Leiden1:=as.character(Leiden1)]

```

# The JEL corpus

We started with all articles identified by the JEL codes from MACRO (ADD EXACT LIST) up until 2012. (Shoud we stop the corpus after 2010 ?).

This gaves us 105 333 articles:

```{r, message=FALSE, warning=FALSE, error=FALSE, results=TRUE, cache=FALSE}
dt_JEL_Articles <- readRDS("Corpus_Econlit/dt_JEL_Articles.rds")
nrow(dt_JEL_Articles)


```

With the following distribution :

```{r, message=FALSE, warning=FALSE, error=FALSE, results=TRUE, cache=FALSE}
ggplot(dt_JEL_Articles, aes(as.numeric(Year.V1))) + 
  geom_bar()


```

## Matching with Web of Science

We matched our list of articles with the Web of Science data base using two techniques:  

1. We matched articles that shared the same year of publication, journal name, pages number and volume number resulting  
We matched **35 378 articles**
  
2. We harmonized the title of the articles on WoS and our JEL corpus by removing special symbols (! ? ;), extra white spaces, and having all title as lowercase.  
We also removed all articles with Title containing less than three words to limit mismatching of articles with very short names.  
We matched **40 433 articles**
  
3. Finally, we brought the two corpus together and only kept unique articles, for a total of **44 833 unique articles**.

The growth rate of the corpus is similar, therefore there is probably not a lot of mismatching

```{r, message=FALSE, warning=FALSE, error=FALSE, results=TRUE, cache=FALSE}
JEL_matched_corpus_nodes <- readRDS("Corpus_Econlit_Matched_WoS/JEL_matched_corpus_nodes.rds")
nrow(JEL_matched_corpus_nodes)


```

```{r, message=FALSE, warning=FALSE, error=FALSE, results=TRUE, cache=FALSE}
ggplot(JEL_matched_corpus_nodes, aes(Annee_Bibliographique)) + 
  geom_bar()


```


# Extending the corpus 

## Finding the Core

The first step to extended our corpus beyond JEL codes, is to find the core references of our corpus. We first find the most referenced articles and defined a threshold to keep only relevant articles. The threshold is found by looking for a point of inflection in the growth rate of the corpus given different thresholds).

We chose a threshold of **9** giving us **16 822** articles, **13 670** articles of which are on WoS.

```{r, message=FALSE, warning=FALSE, error=FALSE, results=TRUE, cache=FALSE}

tresholds_core.png <- readPNG('Corpus_Extended/tresholds_core.png')
grid.raster(tresholds_core.png)

```


## Extending the Core

From this Core, we find all relevant articles to macro. These articles are not necessarily macro per se, but they are relevant to understand the structural relationships that make macro.

We follow the same procedure and find a relevant threshold for the most cited articles by our Core, but also for the articles citing our Core the most:

1. For citations to the core we chose a threshold of **6**, and matched **88 425 articles**

2. For references of the core we chose a threshold of **7**, and giving us  **8 213 articles**, **6 819** articles of which are on WoS.

```{r, message=FALSE, warning=FALSE, error=FALSE, results=TRUE, cache=FALSE}

tresholds_citations_to_core.png <- readPNG('Corpus_Extended/tresholds_citations_to_core.png')
grid.raster(tresholds_citations_to_core.png)

```


```{r, message=FALSE, warning=FALSE, error=FALSE, results=TRUE, cache=FALSE}

tresholds_references_to_core.png <- readPNG('Corpus_Extended/tresholds_references_to_core.png')
grid.raster(tresholds_references_to_core.png)

```



