---
author: "Aurélien Goutsmedt and Alexandre Truc"
date: "Last compiled on `r format(Sys.Date())`"
output: 
  rmdformats::material:
    fig_width: 9
    fig_height: 8
    number_sections: true
    code_folding: hide
    df_print: paged
    thumbnails: true
    lightbox: true
    gallery: true
    css: material_alt.css
editor_options: 
  chunk_output_type: inline
---

```{r, setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = TRUE, cache=FALSE, dev = "png")

```



```{r packages, eval = TRUE}
#%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%#
############################## PART I: LOADING PACKAGES, PATH AND DATA ####################################--------------
#%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%#

##################### Packages, paths, etc. ############################################--------------

source(path.expand("~/macro_AA/functions/functions_for_network_analysis.R"))
source(path.expand("~/macro_AA/Static_Network_Analysis/Script_paths_and_basic_objects.R"))

##################### Loading Data ############################################--------------
nodes_JEL <- readRDS(paste0(data_path,"JEL_matched_corpus_nodes.rds"))
nodes_old_JEL <- readRDS(paste0(data_path,"Old_JEL_matched_corpus_nodes.rds"))
nodes_JEL <- rbind(nodes_JEL,nodes_old_JEL)

edges_JEL <- readRDS(paste0(data_path,"JEL_matched_corpus_edges.rds"))
edges_old_JEL <- readRDS(paste0(data_path,"Old_JEL_matched_corpus_edges.rds"))
edges_JEL <- rbind(edges_JEL,edges_old_JEL)

authors_JEL <- readRDS(paste0(data_path,"JEL_matched_corpus_authors.rds"))
authors_old_JEL <- readRDS(paste0(data_path,"Old_JEL_matched_corpus_authors.rds"))
authors_JEL <- rbind(authors_JEL,authors_old_JEL)

institutions_info_JEL <- fread(paste0(data_path,"Macro_AA_Institutions_Cleaned.csv"), quote="", fill = TRUE) %>% data.table()

ref_info_JEL <- readRDS(paste0(data_path,"JEL_matched_corpus_references_info.rds"))
ref_info_old_JEL <- readRDS(paste0(data_path,"Old_JEL_matched_corpus_references_info.rds"))
ref_info_JEL <- unique(rbind(ref_info_JEL,ref_info_old_JEL))

# keepint only refs with a title and a ESpecialite, then removing doublons
ref_info_JEL <- unique(ref_info_JEL[Titre != "NA" & ESpecialite != "NA",c("New_id2","Titre","ESpecialite")])
doublons <- which(duplicated(ref_info_JEL$New_id2))

if(length(doublons) != 0){
  ref_info_JEL <- ref_info_JEL[-doublons]
}


# Adding info to references
edges_JEL <- merge(unique(edges_JEL),unique(ref_info_JEL[Titre != "NA" & ESpecialite != "NA",c("New_id2","Titre","ESpecialite")]), by = "New_id2", all.x = TRUE)
edges_JEL <- merge(edges_JEL,unique(nodes_JEL[,c("ID_Art","Annee_Bibliographique")]), by = "ID_Art", all.x = TRUE)

# Adding institutions to Articles
institutions_info_JEL$ID_Art <- as.integer(institutions_info_JEL$ID_Art)
institutions_info_JEL$Ordre <- as.integer(institutions_info_JEL$Ordre)
authors_JEL <- merge(unique(authors_JEL),unique(institutions_info_JEL), by = c("ID_Art","Ordre"), all.x = TRUE)

# removing useless files

rm(ref_info_JEL)
rm(institutions_info_JEL)

# passing name column to upper letters
edges_JEL <- edges_JEL[, Nom := toupper(Nom)]
authors_JEL <- authors_JEL[, Nom := toupper(Nom)]
nodes_JEL <- nodes_JEL[, Nom := toupper(Nom)]

# Fixing the subperiod
start_date <- c(1970,1977,1984,1991,1997,2003)
end_date <- c(1976,1983,1990,1996,2002,2008)

# i = 1 # choosing the period to study

title_var <- paste0("Network Analysis for ",start_date[i],"-",end_date[i])
```

---
title: `r title_var`
---

# Bibliographic Coupling 

```{r,  eval = TRUE}
graph_coupling <- readRDS(paste0(graph_data_path,"graph_coupling_",start_date[i],"-",end_date[i],".rds"))

```

To run the Leiden partition algorithm and the Force Atlas algorithm (see below), we sometimes need to reduce the number of nodes and links in our network. We try to set relevant thresholds for our purpose, while keeping the network as big as possible when necessary, in the limits of our calculation capacities.  

For the bibliographic coupling network, first, we have kept all the JEL articles that has been cited at least `r unique(V(graph_coupling)$threshold)`. Second, for tractability, we have kept the links between two JEL articles, only if they share at least `r unique(E(graph_coupling)$threshold)` references.

## Projecting the Graph


```{r,  eval = TRUE}

include_graphics(path.expand(paste0(picture_path,"graph_coupling_",start_date[i],"-",end_date[i],".png")))
```

## Basic Statistics on communities

Follows a table summarizing major information about the communities of the bibliographic coupling network.  

To see how communities are positionned on the graph below, just look at the label of the most cited nodes in the table, and spot it on the graph.  


```{r, message=FALSE, warning=FALSE, error=FALSE, results=TRUE, cache=FALSE,  eval = TRUE}

# Extracting the nodes of the network
Nodes_coupling <- graph_coupling %>%
  activate(nodes)%>%
  select(Id, Annee_Bibliographique,Label,nb_cit,Com_ID,Revue,ESpecialite) %>%
  as.data.table()

# Changing format of ID_Art to merge with other data table
Nodes_coupling$ID_Art <- as.integer(Nodes_coupling$Id)

# Calculating the size of communities and mean of citation per community (total number of citations of all the nodes on the number of nodes)
Nodes_coupling <- Nodes_coupling[, size_com := .N, by = "Com_ID"][, mean_cit_com := sum(nb_cit), by = "Com_ID"][, mean_cit_com := mean_cit_com/size_com]

# keeping only communities with at least x% of the nodes
Nodes_coupling <- Nodes_coupling[, share_com := size_com/length(Nodes_coupling$ID_Art)][share_com >= 0.01,]

# Merging with the authors table, to have the complete list
references_extended <- merge(Nodes_coupling,authors_JEL[,c("ID_Art","Nom","Titre","Ordre","Institution","Pays")], by = "ID_Art")

# Merging with the reference table
# We now have the nodes, with community information, plus the references cited by these nodes
references_extended <- merge(references_extended,edges_JEL[,c("ID_Art","New_id2","Annee","Nom","Revue_Abbrege","Titre")], by = "ID_Art")

# Renaming columns to avoid confusion
setnames(references_extended,c("Nom.x","Nom.y","Titre.x","Titre.y"), c("citing_author","cited_author","Titre","Cited_Title"))

# Strategy: keeping the five highest values for different variables, per community
# fixing n
n = 10

# Keeping the n nodes with the highest number of citations in our corpus, per community
most_cited_nodes <- unique(references_extended[, c("Com_ID","nb_cit","Label","Titre")])
most_cited_nodes <- most_cited_nodes %>%
  group_by(Com_ID) %>%
  arrange(desc(nb_cit)) %>%
  slice(1:n)

# Keeping the n references the most cited per community
most_cited_ref <- references_extended[, c("Com_ID","New_id2","cited_author","Annee","Revue_Abbrege","Cited_Title")]

# calculating the nb of citations of a ref in the whole corpus and per community, then dividing each of the two values by the total number of refs, and the total number of refs per com, to have the total frequency, and the frequency per com
most_cited_ref <- most_cited_ref[, nb_cit_ref_com := .N, by = c("Com_ID","New_id2")][, nb_cit_ref := .N, by = "New_id2"][, nb_cit_per_com := .N, by = "Com_ID"][, total_nb_cit := .N][, com_freq := nb_cit_ref_com/nb_cit_per_com][, total_freq := nb_cit_ref/total_nb_cit]
most_cited_ref <- most_cited_ref[,norm_dev_ref := sqrt(length(unique(references_extended$ID_Art)))*(com_freq - total_freq)/sqrt(total_freq*(1-total_freq))]
most_cited_ref <- most_cited_ref %>%
  select(Com_ID,New_id2,cited_author,Annee,Revue_Abbrege,Cited_Title,com_freq,norm_dev_ref) %>%
  unique()

  
doublons <- which(duplicated(most_cited_ref[,c("Com_ID","New_id2")]))

if(length(doublons) != 0){
  most_cited_ref <- most_cited_ref[-doublons]
}

abs_most_cited_ref <-  most_cited_ref %>%
  select(Com_ID,cited_author,Annee,Revue_Abbrege,Cited_Title,com_freq) %>%
  group_by(Com_ID) %>%
  arrange(desc(com_freq)) %>%
  slice(1:n) %>%
  as.data.table()

re_most_cited_ref <- most_cited_ref %>%
  group_by(Com_ID) %>%
  arrange(desc(norm_dev_ref)) %>%
  slice(1:n) %>%
  rename(cited_author_dev = cited_author, Annee_dev = Annee, Revue_Abbrege_dev = Revue_Abbrege, Cited_Title_dev = Cited_Title)%>%
  as.data.table()

most_cited_ref <-  cbind(abs_most_cited_ref,re_most_cited_ref[,c("cited_author_dev","Annee_dev","Revue_Abbrege_dev","Cited_Title_dev","norm_dev_ref")])

# keeping the n authors the most present in coupling communities
main_author <- unique(references_extended[, c("ID_Art","Com_ID","citing_author")])
main_author <- main_author[, main_author := .N, by = c("Com_ID","citing_author")]
main_author <- main_author %>%
  select(Com_ID,citing_author,main_author) %>%
  unique() %>%
  group_by(Com_ID) %>%
  arrange(desc(main_author)) %>%
  slice(1:n)

# keeping the n journals where most nodes were published in coupling communities
main_journal <- unique(Nodes_coupling[, c("ID_Art","Com_ID","Revue")])
main_journal <- main_journal[, freq := .N, by = "Revue"][, freq_com := .N, by = c("Com_ID","Revue")][, total := .N][, total_com := .N, by = "Com_ID"][, freq := freq/total][, freq_com := freq_com/total_com]
main_journal <- main_journal[freq_com > 0.00,norm_dev_journal := sqrt(length(unique(references_extended$ID_Art)))*((freq_com - freq)/sqrt(freq*(1-freq)))]
main_journal <- main_journal %>%
  select(Com_ID,Revue,freq_com,norm_dev_journal) %>%
  unique() %>%
  group_by(Com_ID) %>%
  arrange(desc(norm_dev_journal)) %>%
  slice(1:n) %>%
  rename(main_journal = Revue)

# keeping the n top disciplines per community
main_discipline <- unique(Nodes_coupling[, c("ID_Art","Com_ID","ESpecialite")])
main_discipline <- main_discipline[, freq := .N, by = "ESpecialite"][, freq_com := .N, by = c("Com_ID","ESpecialite")][, total := .N][, total_com := .N, by = "Com_ID"][, freq := freq/total][, freq_com := freq_com/total_com]
main_discipline <- main_discipline[,norm_dev_discipline := sqrt(length(unique(references_extended$ID_Art)))*(freq_com - freq)/sqrt(freq*(1-freq))]
main_discipline <- main_discipline %>%
  select(Com_ID,ESpecialite,norm_dev_discipline) %>%
  unique() %>%
  group_by(Com_ID) %>%
  arrange(desc(norm_dev_discipline)) %>%
  slice(1:n) %>%
  as.data.table()

main_discipline <- main_discipline[, rank := 1:.N, by = list(Com_ID)]

# keeping the n institutions the most present in coupling communities

  main_institution <- unique(references_extended[, c("ID_Art","Com_ID","Institution")])
  main_institution <- main_institution[, total_com := .N, by = "Com_ID"][, total := .N][Institution != "NA"]
  main_institution <- main_institution[,freq := .N, by = "Institution"][, freq_com := .N, by = c("Com_ID","Institution")][, freq := freq/total][, freq_com := freq_com/total_com]
  main_institution <- main_institution[freq_com > 0.005, norm_dev_institution := sqrt(length(unique(references_extended[, c("ID_Art","Com_ID","Institution")])$ID_Art))*((freq_com - freq)/sqrt(freq*(1-freq)))]
  
  main_institution <- main_institution %>%
    select(Com_ID,Institution,freq_com,norm_dev_institution) %>%
    unique()
  
  abs_main_institution <-  main_institution %>%
    select(Com_ID,Institution,freq_com) %>%
    group_by(Com_ID) %>%
    arrange(desc(freq_com)) %>%
    slice(1:n) %>%
    as.data.table()
  
  re_main_institution <- main_institution %>%
    group_by(Com_ID) %>%
    arrange(desc(norm_dev_institution)) %>%
    slice(1:n) %>%
    rename(Institution_dev = Institution)%>%
    as.data.table()
  
  main_institution <-  cbind(abs_main_institution,re_main_institution[,c("Institution_dev","norm_dev_institution")])
  
  main_institution <- main_institution[, rank := 1:.N, by = list(Com_ID)]


# keeping the n institutions the most present in coupling communities

  main_country <- unique(references_extended[, c("ID_Art","Com_ID","Pays")])
  main_country <- main_country[, total_com := .N, by = "Com_ID"][, total := .N][Pays != "NA"]
  main_country <- main_country[,freq := .N, by = "Pays"][, freq_com := .N, by = c("Com_ID","Pays")][, freq := freq/total][, freq_com := freq_com/total_com]
  main_country <- main_country[freq_com > 0.01, norm_dev_pays := sqrt(length(unique(references_extended[, c("ID_Art","Com_ID","Pays")])$ID_Art))*((freq_com - freq)/sqrt(freq*(1-freq)))]
  main_country <- main_country %>%
    select(Com_ID,Pays,freq_com,norm_dev_pays) %>%
    unique() %>%
    group_by(Com_ID) %>%
    arrange(desc(norm_dev_pays)) %>%
    filter(norm_dev_pays != "NA") %>%
    slice(1:n) %>%
    as.data.table()

  main_country <- main_country[, rank := 1:.N, by = list(Com_ID)]


# creating a "rank" column to be merged with the data
rank <- data.table(rank=1:n)
rank <- merge(unique(Nodes_coupling$Com_ID), rank)
colnames(rank)[1] = "Com_ID"
rank <- rank %>% arrange(Com_ID)

# Merging all the data on coupling communities
coupling_com <- merge(unique(Nodes_coupling[,c("Com_ID","share_com")]), rank, by = "Com_ID")
coupling_com <- cbind(coupling_com,most_cited_nodes[, c("Label","Titre","nb_cit")],
                      most_cited_ref[, c("cited_author","Annee","Revue_Abbrege","Cited_Title","com_freq","cited_author_dev","Annee_dev","Revue_Abbrege_dev","Cited_Title_dev","norm_dev_ref")], 
                      main_author[, c("citing_author","main_author")], main_journal[, c("main_journal","norm_dev_journal")])

  coupling_com <- merge(coupling_com, main_institution, by = c("Com_ID","rank"), all.x = TRUE)
  coupling_com <- merge(coupling_com, main_country[,c("Com_ID","rank","Pays","norm_dev_pays")], by = c("Com_ID","rank"), all.x = TRUE)


coupling_com <- merge(coupling_com, main_discipline, by = c("Com_ID","rank"), all.x = TRUE)

# Projecting the table with all these data

datatable(coupling_com, rownames = TRUE, 
          options =  list(scrollY = "640px",
  scrollCollapse = TRUE,
  scrollX = "400px",
  paging = FALSE))
```

## TF-IDF on communities

```{r, fig.width = 17, fig.height = 13,  eval = TRUE}

TF_IDF <- readRDS(paste0(graph_data_path,"tf-idf_coupling_",start_date[i],"-",end_date[i],".rds"))

TF_IDF$plot
```

## Analyzing relations between coupling communities

```{r, fig.width = 13, fig.height = 10, eval = TRUE, message = FALSE}
############################# Projection of the graph #########################

# loading the graph if necessary
graph_coupling_community <- readRDS(paste0(graph_data_path,"graph_coupling_community_",start_date[i],"-",end_date[i],".rds"))

# Plotting the graph  
ggraph(graph_coupling_community, "manual", x = x, y = y) + 
  geom_edge_arc(aes(width = weight), color = "Black", alpha = 0.3, strength = 0.2, show.legend = FALSE) +
  scale_edge_width_continuous(range = c(0.1,10)) +
  geom_node_point(aes(x=x, y=y, size = size, fill = color), pch = 21, alpha = 0.9, show.legend = FALSE) +
  scale_size_continuous(range = c(1,30)) +
  scale_fill_identity() +
  scale_edge_colour_identity() +
  geom_label_repel(aes(x=x, y=y, label = Id, fill = color), size = 3, fontface="bold", alpha = 1, point.padding=NA, show.legend = FALSE) +
  #scale_size_continuous(range = c(1,4)) +
  theme_void() +
  ggsave(paste0(picture_path,"graph_coupling_community_",start_date[i],"-",end_date[i],".png"), width=20, height=20, units = "cm")

```


```{r, fig.height = 12, fig.width = 18,  eval = TRUE, message = FALSE}
# plotting the heatmap with the dendrogram
heatmap <- clustering_communities(graph_coupling_community, label_size = 20, number_size = 10)

png(path.expand(paste0(picture_path,"heatmap_coupling_",start_date[i],"-",end_date[i],".png")), width = 2500, height = 2000, pointsize = 100)
grid.newpage()
print(heatmap$heatmap, vp = viewport(x = 0.4, y = 0.5, width = 0.75, height = 1.0))
print(heatmap$dendrogram, vp = viewport(x = 0.87, y = 0.5, width = 0.2, height = 0.9))
dev.off()

include_graphics(path.expand(paste0(picture_path,"heatmap_coupling_",start_date[i],"-",end_date[i],".png")))
```


## Studying other attributes

```{r, message = FALSE, eval = TRUE}
# Using the function we have built
nodes_coupling <- graph_coupling %>% activate(nodes) %>% as.data.table()
edges_coupling <- graph_coupling %>% activate(edges) %>% as.data.table()


graph_journal <- graph_from_attribute(nodes = nodes_coupling, edges = edges_coupling, palette = mypalette, Attribute_name = "Revue")

# Biggest journal per community
important_journals <- top_ordering(graph_journal, ordering_column = "Size_att", top_n = 12, top_n_com = 1)

# Plotting the graph  
plot_graph_journal <- ggraph(graph_journal, "manual", x = x, y = y) + 
  geom_edge_arc(aes(width = weight, color = color_edges), alpha = 0.3, strength = 0.2, show.legend = FALSE) +
  scale_edge_width_continuous(range = c(0.1,10)) +
  geom_node_point(aes(x=x, y=y, size = size, fill = color), pch = 21, alpha = 0.9, show.legend = FALSE) +
  scale_size_continuous(range = c(0.5,25)) +
  scale_fill_identity() +
  scale_edge_colour_identity() +
  geom_label_repel(data = important_journals, aes(x=x, y=y, label = Id, fill = color), size = 3, fontface="bold", alpha = 1, point.padding=NA, show.legend = FALSE) +
  #scale_size_continuous(range = c(1,4)) +
  theme_void() +
  ggsave(paste0(picture_path,"graph_revue_",start_date[i],"-",end_date[i],".png"), width=25, height=25, units = "cm")

include_graphics(path.expand(paste0(picture_path,"graph_revue_",start_date[i],"-",end_date[i],".png")))
```

```{r, message=FALSE, warning=FALSE, error=FALSE, results=TRUE, cache=FALSE,  eval = TRUE}
# Biggest journal per community to be displayed
journal_table <- top_ordering(graph_journal, ordering_column = "Size_att", top_n = 20, top_n_com = 5)
journal_table <- journal_table[order(Com_ID),1:3]

datatable(journal_table, rownames = TRUE, 
          options =  list(scrollY = "640px",
  scrollCollapse = TRUE,
  scrollX = "400px",
  paging = FALSE))
```


# Bibliographic coupling per authors


```{r, message=FALSE, warning=FALSE, error=FALSE, results=TRUE, cache=FALSE,  eval = TRUE}

# loading the graph if necessary
graph_authors_coupling <- readRDS(paste0(graph_data_path,"graph_authors_coupling_",start_date[i],"-",end_date[i],".rds"))

```

To build the authors network from bibliographic coupling data, first, we have kept all the JEL articles that has been cited at least `r unique(V(graph_authors_coupling)$threshold)`. Second, for tractability, we have kept the links between two authors, only if they share at least `r unique(E(graph_authors_coupling)$threshold)` references in all the JEL articles they have published. The graph has been filtered by keeping only the 

```{r, message=FALSE, warning=FALSE, error=FALSE, results=TRUE, cache=FALSE,  eval = TRUE}

include_graphics(path.expand(paste0(picture_path,"graph_authors_coupling_",start_date[i],"-",end_date[i],".png")))
```

## Analyzing relations between coupling communities

```{r, fig.width = 17, fig.height = 13,  eval = TRUE}

graph_authors_coupling_community <- readRDS( paste0(graph_data_path,"graph_authors_coupling_community_",start_date[i],"-",end_date[i],".rds"))

# Plotting the graph  
plot_graph_authors_coupling_community <- ggraph(graph_authors_coupling_community, "manual", x = x, y = y) + 
  geom_edge_arc(aes(width = weight), color = "Black", alpha = 0.3, strength = 0.2, show.legend = FALSE) +
  scale_edge_width_continuous(range = c(0.1,10)) +
  geom_node_point(aes(x=x, y=y, size = size, fill = color), pch = 21, alpha = 0.9, show.legend = FALSE) +
  scale_size_continuous(range = c(1,30)) +
  scale_fill_identity() +
  scale_edge_colour_identity() +
  geom_label_repel(aes(x=x, y=y, label = Id, fill = color), size = 4, fontface="bold", alpha = 1, point.padding=NA, show.legend = FALSE) +
  #scale_size_continuous(range = c(1,4)) +
  theme_void() +
  ggsave(paste0(picture_path,"graph_authors_coupling_community_",start_date[i],"-",end_date[i],".png"), width=25, height=25, units = "cm")

include_graphics(path.expand(paste0(picture_path,"graph_authors_coupling_community_",start_date[i],"-",end_date[i],".png")))
```


```{r, fig.height= 12, fig.width=18,  eval = TRUE}
# plotting the heatmap with the dendrogram
heatmap <- clustering_communities(graph_authors_coupling_community, label_size = 20, number_size = 10)

png(path.expand(paste0(picture_path,"heatmap_authors_coupling_",start_date[i],"-",end_date[i],".png")), width = 2500, height = 2000)
grid.newpage()
print(heatmap$heatmap, vp = viewport(x = 0.4, y = 0.5, width = 0.75, height = 1.0))
print(heatmap$dendrogram, vp = viewport(x = 0.87, y = 0.5, width = 0.2, height = 0.9))
dev.off()

include_graphics(path.expand(paste0(picture_path,"heatmap_authors_coupling_",start_date[i],"-",end_date[i],".png")))
```


```{r, message=FALSE, warning=FALSE, error=FALSE, results=TRUE, cache=FALSE,  eval = TRUE}

# Extracting the nodes of the network
Nodes_authors_coupling <- graph_authors_coupling %>%
  activate(nodes)%>%
  select(Id, nb_cit_author, nb_art, Com_ID, Size_com) %>%
  filter(Size_com > 0.01) %>%
  as.data.table()

# Merging with the authors table, to have the list of the authors 
Nodes_authors_coupling <- merge(Nodes_authors_coupling,authors_JEL[,c("ID_Art","Nom","Titre","Ordre","Institution","Pays")], by.x = "Id", by.y = "Nom", allow.cartesian = TRUE)

# Merging with the nodes JEL table
# We now have the author-nodes and the artilces they have published between the two dates we have chosen, plus the journal and the discipline
Nodes_authors_coupling <- merge(Nodes_authors_coupling,nodes_JEL[between(Annee_Bibliographique,start_date[i],end_date[i]) ,c("ID_Art","ItemID_Ref","Annee_Bibliographique","Revue","ESpecialite")], by = "ID_Art", allow.cartesian = TRUE)
nb_cit <- edges_JEL[between(Annee_Bibliographique,start_date[i],end_date[i]) & ItemID_Ref != 0][,nb_cit := .N, by = "ItemID_Ref"]
Nodes_authors_coupling <- merge(Nodes_authors_coupling,unique(nb_cit[,c("ItemID_Ref","nb_cit")]), by = "ItemID_Ref", all.x = "TRUE")

# Merging with the reference table
# We now have the nodes, with community information, plus the references cited by these nodes
Nodes_authors_coupling <- merge(Nodes_authors_coupling,edges_JEL[between(Annee_Bibliographique,start_date[i],end_date[i]),c("ID_Art","New_id2","Annee","Nom","Revue_Abbrege","Titre")], by = "ID_Art", allow.cartesian = TRUE)

# Renaming columns to avoid confusion
setnames(Nodes_authors_coupling,c("Nom","Titre.x","Titre.y"), c("cited_author","citing_title","cited_title"))

# Strategy: keeping the five highest values for different variables, per community
# fixing n
n = 10

# Keeping the n nodes with the highest number of citations in our corpus, per community
most_cited_nodes <- unique(Nodes_authors_coupling[, c("Com_ID","nb_cit_author","Id")])
most_cited_nodes <- most_cited_nodes %>%
  group_by(Com_ID) %>%
  arrange(desc(nb_cit_author)) %>%
  slice(1:n) %>%
  as.data.table()

most_cited_nodes <- most_cited_nodes[, rank := 1:.N, by = list(Com_ID)]

# Keeping the n nodes with the highest number of citations in our corpus, per community
most_cited_articles <- unique(Nodes_authors_coupling[, c("Com_ID","nb_cit","ID_Art","citing_title","Revue")])
most_cited_articles <- most_cited_articles %>%
  group_by(Com_ID) %>%
  arrange(desc(nb_cit)) %>%
  slice(1:n)

# keeping the n authors the most present in coupling communities
main_author <- unique(Nodes_authors_coupling[, c("ID_Art","Com_ID","Id","nb_art")])
#main_author <- main_author[, main_author := .N, by = c("Com_ID","Id")]
setnames(main_author, "Id","citing_author")
main_author <- main_author %>%
  select(Com_ID,citing_author,nb_art) %>%
  unique() %>%
  group_by(Com_ID) %>%
  arrange(desc(nb_art)) %>%
  slice(1:n)%>%
  as.data.table()

main_author <- main_author[, rank := 1:.N, by = list(Com_ID)]

# Keeping the n references the most cited per community
most_cited_ref <- Nodes_authors_coupling[, c("Com_ID","New_id2","cited_author","Annee","Revue_Abbrege","cited_title")]
most_cited_ref <- most_cited_ref[, nb_cit_ref_com := .N, by = c("Com_ID","New_id2")][, nb_cit_ref := .N, by = "New_id2"][, nb_cit_per_com := .N, by = "Com_ID"][, total_nb_cit := .N][, com_freq := nb_cit_ref_com/nb_cit_per_com][, total_freq := nb_cit_ref/total_nb_cit]
most_cited_ref <- most_cited_ref[,norm_dev_ref := sqrt(length(unique(references_extended$ID_Art)))*(com_freq - total_freq)/sqrt(total_freq*(1-total_freq))]
most_cited_ref <- most_cited_ref %>%
  select(Com_ID,New_id2,cited_author,Annee,Revue_Abbrege,cited_title,com_freq,norm_dev_ref) %>%
  unique()


doublons <- which(duplicated(most_cited_ref[,c("Com_ID","New_id2")]))

if(length(doublons) != 0){
  most_cited_ref <- most_cited_ref[-doublons]
}

abs_most_cited_ref <-  most_cited_ref %>%
  select(Com_ID,cited_author,Annee,Revue_Abbrege,cited_title,com_freq) %>%
  group_by(Com_ID) %>%
  arrange(desc(com_freq)) %>%
  slice(1:n) %>%
  as.data.table()

re_most_cited_ref <- most_cited_ref %>%
  group_by(Com_ID) %>%
  arrange(desc(norm_dev_ref)) %>%
  slice(1:n) %>%
  rename(cited_author_dev = cited_author, Annee_dev = Annee, Revue_Abbrege_dev = Revue_Abbrege, cited_title_dev = cited_title)%>%
  as.data.table()

most_cited_ref <-  cbind(abs_most_cited_ref,re_most_cited_ref[,c("cited_author_dev","Annee_dev","Revue_Abbrege_dev","cited_title_dev","norm_dev_ref")])

# keeping the n journals where most nodes were published in coupling communities
main_journal <- unique(Nodes_authors_coupling[, c("ID_Art","Com_ID","Revue")])
main_journal <- main_journal[, freq := .N, by = "Revue"][, freq_com := .N, by = c("Com_ID","Revue")][, total := .N][, total_com := .N, by = "Com_ID"][, freq := freq/total][, freq_com := freq_com/total_com]
main_journal <- main_journal[freq_com > 0.00,norm_dev_journal := sqrt(length(unique(references_extended$ID_Art)))*((freq_com - freq)/sqrt(freq*(1-freq)))]
main_journal <- main_journal %>%
  select(Com_ID,Revue,freq_com,norm_dev_journal) %>%
  unique() %>%
  group_by(Com_ID) %>%
  arrange(desc(norm_dev_journal)) %>%
  slice(1:n) %>%
  rename(main_journal = Revue)

# keeping the n top disciplines per community
main_discipline <- unique(Nodes_authors_coupling[, c("ID_Art","Com_ID","ESpecialite")])
main_discipline <- main_discipline[, freq := .N, by = "ESpecialite"][, freq_com := .N, by = c("Com_ID","ESpecialite")][, total := .N][, total_com := .N, by = "Com_ID"][, freq := freq/total][, freq_com := freq_com/total_com]
main_discipline <- main_discipline[,norm_dev_discipline := sqrt(length(unique(references_extended$ID_Art)))*(freq_com - freq)/sqrt(freq*(1-freq))]
main_discipline <- main_discipline %>%
  select(Com_ID,ESpecialite,norm_dev_discipline) %>%
  unique() %>%
  group_by(Com_ID) %>%
  arrange(desc(norm_dev_discipline)) %>%
  slice(1:n) %>%
  as.data.table()

main_discipline <- main_discipline[, rank := 1:.N, by = list(Com_ID)]

# keeping the n institutions the most present in coupling communities

  main_institution <- unique(Nodes_authors_coupling[, c("ID_Art","Com_ID","Id","Institution")])
  main_institution <- main_institution[, total_com := .N, by = "Com_ID"][, total := .N][Institution != "NA"]
  main_institution <- main_institution[,freq := .N, by = "Institution"][, freq_com := .N, by = c("Com_ID","Institution")][, freq := freq/total][, freq_com := freq_com/total_com]
  main_institution <- main_institution[freq_com > 0.005, norm_dev_institution := sqrt(length(unique(references_extended[, c("ID_Art","Com_ID","Institution")])$ID_Art))*((freq_com - freq)/sqrt(freq*(1-freq)))]
  
  main_institution <- main_institution %>%
    select(Com_ID,Institution,freq_com,norm_dev_institution) %>%
    unique()
  
  abs_main_institution <-  main_institution %>%
    select(Com_ID,Institution,freq_com) %>%
    group_by(Com_ID) %>%
    arrange(desc(freq_com)) %>%
    slice(1:n) %>%
    as.data.table()
  
  re_main_institution <- main_institution %>%
    group_by(Com_ID) %>%
    arrange(desc(norm_dev_institution)) %>%
    slice(1:n) %>%
    rename(Institution_dev = Institution)%>%
    as.data.table()
  
  main_institution <-  cbind(abs_main_institution,re_main_institution[,c("Institution_dev","norm_dev_institution")])
  
  main_institution <- main_institution[, rank := 1:.N, by = list(Com_ID)]


# keeping the n institutions the most present in coupling communities
  main_country <- unique(Nodes_authors_coupling[, c("ID_Art","Com_ID","Id","Pays")])
  main_country <- main_country[, total_com := .N, by = "Com_ID"][, total := .N][Pays != "NA"]
  main_country <- main_country[,freq := .N, by = "Pays"][, freq_com := .N, by = c("Com_ID","Pays")][, freq := freq/total][, freq_com := freq_com/total_com]
  main_country <- main_country[freq_com > 0.01, norm_dev_pays := sqrt(length(unique(references_extended[, c("ID_Art","Com_ID","Pays")])$ID_Art))*((freq_com - freq)/sqrt(freq*(1-freq)))]
  main_country <- main_country %>%
    select(Com_ID,Pays,freq_com,norm_dev_pays) %>%
    unique() %>%
    group_by(Com_ID) %>%
    arrange(desc(norm_dev_pays)) %>%
    filter(norm_dev_pays != "NA") %>%
    slice(1:n) %>%
    as.data.table()
  
  main_country <- main_country[, rank := 1:.N, by = list(Com_ID)]


# creating a "rank" column to be merged with the data
rank <- data.table(rank=1:n)
rank <- merge(unique(Nodes_authors_coupling$Com_ID), rank)
colnames(rank)[1] = "Com_ID"
rank <- rank %>% arrange(Com_ID)

# Merging all the data on coupling communities
authors_coupling_com <- merge(unique(Nodes_authors_coupling[,c("Com_ID","Size_com")]), rank, by = "Com_ID")
authors_coupling_com <- merge(authors_coupling_com, most_cited_nodes[, c("Com_ID","rank","Id","nb_cit_author")], by = c("Com_ID","rank"), all.x = TRUE)

authors_coupling_com <- cbind(authors_coupling_com,most_cited_articles[, c("citing_title","Revue","nb_cit")],
                              most_cited_ref[, c("cited_author","Annee","Revue_Abbrege","cited_title","com_freq","cited_author_dev","Annee_dev","Revue_Abbrege_dev","cited_title_dev","norm_dev_ref")], 
                              main_journal[, c("main_journal","norm_dev_journal")])

authors_coupling_com <- merge(authors_coupling_com, main_author[, main_author := citing_author][, c("Com_ID","rank","main_author","nb_art")],  by = c("Com_ID","rank"), all.x = TRUE)


  authors_coupling_com <- merge(authors_coupling_com, main_institution, by = c("Com_ID","rank"), all.x = TRUE)
  authors_coupling_com <- merge(authors_coupling_com, main_country[,c("Com_ID","rank","Pays","norm_dev_pays")], by = c("Com_ID","rank"), all.x = TRUE)


authors_coupling_com <- merge(authors_coupling_com, main_discipline, by = c("Com_ID","rank"), all.x = TRUE)

# Projecting the table with all these data

datatable(authors_coupling_com, rownames = TRUE, 
          options =  list(scrollY = "640px",
  scrollCollapse = TRUE,
  scrollX = "400px",
  paging = FALSE))
```


```{r, fig.width = 17, fig.height = 13,  eval = TRUE}

TF_IDF_authors <- readRDS(paste0(graph_data_path,"tf-idf_authors_coupling_",start_date[i],"-",end_date[i],".rds"))

TF_IDF_authors$plot
```

## Network of Institution from Bibliographic Coupling

```{r, message=FALSE, warning=FALSE, error=FALSE, results=TRUE, cache=FALSE,  eval = TRUE}

  # loading the graph if necessary
graph_institutions_coupling <- readRDS(paste0(graph_data_path,"graph_institutions_coupling_",start_date[i],"-",end_date[i],".rds"))

include_graphics(path.expand(paste0(picture_path,"graph_institutions_coupling_",start_date[i],"-",end_date[i],".png")))

```


```{r, message=FALSE, warning=FALSE, error=FALSE, results=TRUE, cache=FALSE,  eval = TRUE}


institutions_data <- graph_institutions_coupling %>% 
  activate(nodes) %>% 
  as.data.table()
institutions_data <- institutions_data[, share_pays := .N, by = c("Com_ID","Pays")][, total := .N, by = "Com_ID"][, share_pays := share_pays/total]
institutions_data <- unique(institutions_data[order(Com_ID,-share_pays),c("Com_ID","Community_name","Pays","share_pays")])
institutions_data <- institutions_data[, rank:= 1:.N, by = "Com_ID"][rank <= 5]

# Projecting the table with all these data

datatable(institutions_data, rownames = FALSE, 
          options =  list(scrollY = "400px",
  scrollCollapse = TRUE,
  scrollX = "400px",
  paging = FALSE))

```

# Bibliographic Cocitation

## Projecting the Graph

```{r,  eval = TRUE}

graph_cocit <- readRDS(paste0(graph_data_path,"graph_cocit_",start_date[i],"-",end_date[i],".rds"))

```

For the bibliographic cocitation network, first, we have kept all the references that has been cited at least `r print(unique(V(graph_cocit)$threshold))`. Second, for tractability, we have kept the links between two references, only if they were at least `r print(unique(E(graph_cocit)$threshold))` times together.


```{r,  eval = TRUE}

include_graphics(path.expand(paste0(picture_path,"graph_cocit",start_date[i],"-",end_date[i],".png")))
```

## Analyzing the communities of co-citation

```{r, fig.width = 17, fig.height = 13,  eval = TRUE}

# loading the graph if necessary
graph_cocit_community <- readRDS(paste0(graph_data_path,"graph_cocit_community_",start_date[i],"-",end_date[i],".rds"))

# Plotting the graph  
ggraph(graph_cocit_community, "manual", x = x, y = y) + 
  geom_edge_arc(aes(width = weight), color = "Black", alpha = 0.3, strength = 0.2, show.legend = FALSE) +
  scale_edge_width_continuous(range = c(0.1,10)) +
  geom_node_point(aes(x=x, y=y, size = size, fill = color), pch = 21, alpha = 0.9, show.legend = FALSE) +
  scale_size_continuous(range = c(1,30)) +
  scale_fill_identity() +
  scale_edge_colour_identity() +
  geom_label_repel(aes(x=x, y=y, label = Id, fill = color), size = 3, fontface="bold", alpha = 1, point.padding=NA, show.legend = FALSE) +
  #scale_size_continuous(range = c(1,4)) +
  theme_void() +
    ggsave(paste0(picture_path,"graph_cocit_community_",start_date[i],"-",end_date[i],".png"), width=20, height=20, units = "cm")


```

```{r, fig.width = 17, fig.height = 13,  eval = TRUE}

TF_IDF_cocit <- readRDS(paste0(graph_data_path,"tf-idf_cocit_",start_date[i],"-",end_date[i],".rds"))

TF_IDF_cocit$plot
```

```{r, message=FALSE, warning=FALSE, error=FALSE, results=TRUE, cache=FALSE,  eval = TRUE}
# plotting the heatmap with the dendrogram
heatmap <- clustering_communities(graph_cocit_community, label_size = 20, number_size = 10)

png(path.expand(paste0(picture_path,"heatmap_cocit_",start_date[i],"-",end_date[i],".png")), width = 2500, height = 2000)
grid.newpage()
print(heatmap$heatmap, vp = viewport(x = 0.4, y = 0.5, width = 0.75, height = 1.0))
print(heatmap$dendrogram, vp = viewport(x = 0.87, y = 0.5, width = 0.2, height = 0.9))
dev.off()

include_graphics(path.expand(paste0(picture_path,"heatmap_cocit_",start_date[i],"-",end_date[i],".png")))
```


```{r, message=FALSE, warning=FALSE, error=FALSE, results=TRUE, cache=FALSE,  eval = TRUE}

# Extracting the nodes of the network
Nodes_cocit <- graph_cocit %>%
  activate(nodes)%>%
  select(Com_ID, Size_com, Id, Label, Nom, Titre, nb_cit, Revue_Abbrege, ESpecialite) %>%
  as.data.table()

# Changing format of ID_Art to merge with other data table
Nodes_cocit$ID_Art <- as.integer(Nodes_cocit$Id)

# Calculating the size of communities and mean of citation per community (total number of citations of all the nodes on the number of nodes)
Nodes_cocit <- Nodes_cocit[, nb_nodes := .N, by = "Com_ID"][, mean_cit_com := sum(nb_cit), by = "Com_ID"][, mean_cit_com := mean_cit_com/nb_nodes]

# keeping only communities with at least x% of the nodes
Nodes_cocit <- Nodes_cocit[Size_com >= 0.01,]

# Strategy: keeping the five highest values for different variables, per community
# fixing n
n = 10

# Keeping the n nodes with the highest number of citations in our corpus, per community
most_cited_nodes <- unique(Nodes_cocit[, c("Com_ID","nb_cit","Label","Titre","Revue_Abbrege")])
most_cited_nodes <- most_cited_nodes %>%
  group_by(Com_ID) %>%
  arrange(desc(nb_cit)) %>%
  slice(1:n) %>%
  as.data.table()

most_cited_nodes <- most_cited_nodes[, rank := 1:.N, by = list(Com_ID)]

# keeping the n authors the most present in coupling communities
main_author <- unique(Nodes_cocit[, c("Id","Com_ID","Nom")])
main_author <- main_author[, main_author := .N, by = c("Com_ID","Nom")]
main_author <- main_author %>%
  select(Com_ID,Nom,main_author) %>%
  unique() %>%
  group_by(Com_ID) %>%
  arrange(desc(main_author)) %>%
  slice(1:n)%>%
  as.data.table()

main_author <- main_author[, rank := 1:.N, by = list(Com_ID)]

# keeping the n journals where most nodes were published in coupling communities
main_journal <- unique(Nodes_cocit[, c("Id","Com_ID","Revue_Abbrege","nb_nodes")])
main_journal <- main_journal[Revue_Abbrege != "NA", main_journal := .N, by = c("Com_ID","Revue_Abbrege")][, main_journal:= main_journal/nb_nodes]
main_journal <- main_journal %>%
  select(Com_ID,Revue_Abbrege,main_journal) %>%
  unique() %>%
  group_by(Com_ID) %>%
  arrange(desc(main_journal)) %>%
  slice(1:n)%>%
  as.data.table()

main_journal <- main_journal[, rank := 1:.N, by = list(Com_ID)]

# keeping the n top disciplines per community
main_discipline <- unique(Nodes_cocit[, c("Id","Com_ID","ESpecialite","nb_nodes")])
main_discipline <- main_discipline[ESpecialite != "NA", main_discipline := .N, by = c("Com_ID","ESpecialite")][, main_discipline := main_discipline/nb_nodes][main_discipline != "NA"]
main_discipline <- main_discipline %>%
  select(Com_ID,ESpecialite,main_discipline) %>%
  unique() %>%
  group_by(Com_ID) %>%
  arrange(desc(main_discipline)) %>%
  slice(1:n) %>%
  as.data.table()

main_discipline <- main_discipline[, rank := 1:.N, by = list(Com_ID)]

# creating a "rank" column to be merged with the data
rank <- data.table(rank=1:n)
rank <- merge(unique(Nodes_cocit$Com_ID), rank)
colnames(rank)[1] = "Com_ID"
rank <- rank %>% arrange(Com_ID)

# Merging all the data on coupling communities
cocit_com <- merge(unique(Nodes_cocit[,c("Com_ID","Size_com","mean_cit_com")]), rank, by = "Com_ID")

cocit_com <- merge(cocit_com,most_cited_nodes[,c("Com_ID","rank","Label","Titre","Revue_Abbrege","nb_cit")], by = c("Com_ID","rank"), all.x = TRUE)
cocit_com <- merge(cocit_com,main_author, by = c("Com_ID","rank"), all.x = TRUE)
cocit_com <- merge(cocit_com,main_journal, by = c("Com_ID","rank"), all.x = TRUE)
cocit_com <- merge(cocit_com,main_discipline, by = c("Com_ID","rank"), all.x = TRUE)

# Projecting the table with all the data
datatable(cocit_com, rownames = TRUE, 
          options =  list(scrollY = "640px",
  scrollCollapse = TRUE,
  scrollX = "400px",
  paging = FALSE))
```

# Co-authorship Network

## Projecting the Graph

```{r, message=FALSE, warning=FALSE, error=FALSE, results=TRUE, cache=FALSE,  eval = TRUE}

graph_coauthorship <- readRDS(paste0(graph_data_path,"graph_coauthorship_",start_date[i],"-",end_date[i],".rds"))

include_graphics(path.expand(paste0(picture_path,"graph_coauthorship_",start_date[i],"-",end_date[i],".png")))

```


## Network of institutions, from co-authorship data

```{r, message=FALSE, warning=FALSE, error=FALSE, results=TRUE, cache=FALSE,  eval = TRUE}

graph_institutions <-  readRDS(paste0(graph_data_path,"graph_co-authorship_institutions_",start_date[i],"-",end_date[i],".rds"))

include_graphics(path.expand(paste0(picture_path,"graph_co-authorship_institutions_",start_date[i],"-",end_date[i],".png")))

```


```{r, message=FALSE, warning=FALSE, error=FALSE, results=TRUE, cache=FALSE,  eval = TRUE}

data_institutions <- graph_institutions %>%
  activate(nodes) %>%
  filter(Size_com > 0.03) %>%
  select(Com_ID, Size_com, Id, Pays, nb_art) %>%
  arrange(desc(nb_art)) %>% 
  group_by(Com_ID) %>%
  slice(1:6) %>% 
  ungroup() %>%
  arrange(Com_ID) %>%
  as.data.table()

# Projecting the table with all these data

datatable(data_institutions, rownames = FALSE, 
          options =  list(scrollY = "400px",
  scrollCollapse = TRUE,
  scrollX = "400px",
  paging = FALSE))

```


# Studying the relations between the different networks

## Linking the coupling and cocitation networks

```{r, fig.height= 10, fig.width=15,  eval = TRUE}

############sankey diagram cocit/coupling-------------
# Loading the cocit and coupling graph if necessary
#graph_cocit <- readRDS(paste0(graph_data_path,"graph_cocit_",start_date[i],"-",end_date[i],".rds"))
#graph_coupling <- readRDS(paste0(graph_data_path,"graph_coupling_",start_date[i],"-",end_date[i],".rds"))

# extracting the cocit nodes
nodes_cocit <- graph_cocit %>%
  activate(nodes) %>%
 filter(Size_com > 0.01) %>%
  select(Id, Community_name, Label,color) %>%
  as.data.table()

# merging the cocit nodes with the papers which cite them
nodes_cocit$Id <- as.integer(nodes_cocit$Id)
nodes_cocit <- merge(nodes_cocit, edges_JEL[between(Annee_Bibliographique, start_date[i],end_date[i]) & New_id2 %in% nodes_cocit$Id, c("New_id2","ID_Art","ItemID_Ref")], by.x = "Id", by.y = "New_id2") 

# exctracting the coupling nodes
nodes_coupling <- graph_coupling %>%
  activate(nodes) %>%
  filter(Size_com > 0.01) %>%
  select(Id, Community_name, Label,color) %>%
  as.data.table()

# Merging the coupling and cocit data
nodes_coupling$Id <- as.integer(nodes_coupling$Id)
sankey_data <- merge(nodes_cocit,nodes_coupling, by.x="ID_Art", by.y = "Id")

# changing the column names and the name of communities
setnames(sankey_data, c("Id","Community_name.x","Label.x","Community_name.y","Label.y","color.x","color.y"), c("New_id2",
                                                                                                                 "Com_ID_cocit","Label_cocit","Com_ID_coupling","Label_coupling","color_cocit","color_coupling"))
sankey_data$Com_ID_cocit <- paste0("Cct ", sankey_data$Com_ID_cocit)
sankey_data$Com_ID_coupling <- paste0("Cplg ",sankey_data$Com_ID_coupling)
sankey_data <- unique(sankey_data[, value:= .(.N), by = c("Com_ID_coupling","Com_ID_cocit")][,c("Com_ID_coupling",
                                                                                                "Com_ID_cocit","value","color_cocit","color_coupling")])
#sankey_data <- reshape2::melt(sankey_data)
sankey_data <- gather_set_data(sankey_data, 1:2)

# preparing the two color palettes
palette_coupling <- unique(sankey_data[order(Com_ID_coupling),c("Com_ID_coupling","color_coupling")])
palette_cocit <- unique(sankey_data[order(Com_ID_cocit),c("Com_ID_cocit","color_cocit")])
palette <- rbind(palette_coupling,palette_cocit, use.names=FALSE)
setnames(palette, c("Com_ID_coupling","color_coupling"),c("Com_ID","color"))
sankey_data <- merge(sankey_data,palette, by.x = "y", by.y= "Com_ID")

#ordering x to have the coupling communities on the left
sankey_data$x <- factor(x = sankey_data$x,
                        levels = sort(unique(sankey_data$x), decreasing = TRUE), 
                        ordered = TRUE)

# plotting the graph
ggplot(sankey_data, aes(x, id = id, split = y, value = value)) +
  geom_parallel_sets(aes(fill = color_cocit), alpha = 0.5, axis.width = 0.1, show.legend = FALSE) +
  geom_parallel_sets_axes(aes(fill = color), axis.width = 0.3, show.legend = FALSE) +
  scale_fill_identity() +
  theme_void() +
  geom_parallel_sets_labels(colour = 'black', fontface = "bold", angle = 0, size = 4)


```

```{r, fig.height= 10, fig.width=15,  eval = TRUE}

############sankey diagram cocit/coupling-------------
# Loading the cocit and coupling graph if necessary
#graph_authors_coupling <- readRDS(paste0(graph_data_path,"graph_authors_coupling_",start_date[i],"-",end_date[i],".rds"))
#graph_coupling <- readRDS(paste0(graph_data_path,"graph_coupling_",start_date[i],"-",end_date[i],".rds"))

# extracting the cocit nodes
nodes_authors <- graph_authors_coupling %>%
  activate(nodes) %>%
  filter(Size_com > 0.01) %>%
  select(Id, Community_name, color) %>%
  as.data.table()

# merging the cocit nodes with the papers which cite them
nodes_authors <- merge(nodes_authors, unique(authors_JEL[between(Annee_Bibliographique, start_date[i],end_date[i]) & Nom %in% nodes_authors$Id, c("Nom","ID_Art")]), by.x = "Id", by.y = "Nom", allow.cartesian = TRUE) 

# exctracting the coupling nodes
nodes_coupling <- graph_coupling %>%
  activate(nodes) %>%
  filter(Size_com > 0.01) %>%
  select(Id, Community_name, Label,color) %>%
  as.data.table()

# Merging the coupling and cocit data
nodes_coupling$Id <- as.integer(nodes_coupling$Id)
sankey_data <- merge(nodes_authors,nodes_coupling, by.x="ID_Art", by.y = "Id", allow.cartesian = TRUE)

# changing the column names and the name of communities
setnames(sankey_data, c("Id","Community_name.x","Community_name.y","color.x","color.y"), c("Author",
                                                                                    "Com_ID_author","Com_ID_coupling","color_author","color_coupling"))
#sankey_data$Com_ID_cocit <- paste0("Cct ", sankey_data$Com_ID_cocit)
#sankey_data$Com_ID_coupling <- paste0("Cplg ",sankey_data$Com_ID_coupling)
sankey_data <- unique(sankey_data[, value:= .(.N), by = c("Com_ID_coupling","Com_ID_author")][,c("Com_ID_coupling",
                                                                                                "Com_ID_author","value","color_author","color_coupling")])
#sankey_data <- reshape2::melt(sankey_data)
sankey_data <- gather_set_data(sankey_data, 1:2)

# preparing the two color palettes
palette_coupling <- unique(sankey_data[order(Com_ID_coupling),c("Com_ID_coupling","color_coupling")])
palette_author <- unique(sankey_data[order(Com_ID_author),c("Com_ID_author","color_author")])

# preparing the two color palettes
palette_coupling <- unique(sankey_data[order(Com_ID_coupling),c("Com_ID_coupling","color_coupling")])
palette_author <- unique(sankey_data[order(Com_ID_author),c("Com_ID_author","color_author")])
palette <- rbind(palette_coupling,palette_author, use.names=FALSE)
setnames(palette, c("Com_ID_coupling","color_coupling"),c("Com_ID","color"))
sankey_data <- merge(sankey_data,unique(palette), by.x = "y", by.y= "Com_ID")

#ordering x to have the coupling communities on the left
sankey_data$x <- factor(x = sankey_data$x,
                        levels = sort(unique(sankey_data$x), decreasing = TRUE), 
                        ordered = TRUE)

# plotting the graph
ggplot(sankey_data, aes(x, id = id, split = y, value = value)) +
  geom_parallel_sets(aes(fill = color_author), alpha = 0.5, axis.width = 0.1, show.legend = FALSE) +
  geom_parallel_sets_axes(aes(fill = color), axis.width = 0.3, show.legend = FALSE) +
  scale_fill_identity() +
  theme_void() +
  geom_parallel_sets_labels(colour = 'black', fontface = "bold", angle = 0, size = 4)


```


# Deconstructing Leiden Communities for Coupling

## List of the communities for different resolution

```{r, fig.height= 10, fig.width=15,  eval = TRUE}
Leiden_coupling <- readRDS(paste0(graph_data_path,"Leiden_coupling_",start_date[i],"-",end_date[i],".rds")) %>% as.data.table()
resolution_set = c(2,1.5,1,0.5)

# identifying the most cited nodes per resolution

# Separing community name and size of communities for different resolution, to bind them by rows
All_com <- data.table()
  for(j in 1:(length(resolution_set))){
    Com <- Leiden_coupling[,.SD,.SDcols=c(1,grep("Community_name",colnames(Leiden_coupling))[j],grep("Size_com",colnames(Leiden_coupling))[j])]
    Com$Resolution <- gsub(".*_","",colnames(Leiden_coupling[,.SD,.SDcols=grep("Community_name",colnames(Leiden_coupling))[j]]))

    All_com <- rbind(All_com,Com, use.names = FALSE)
  }

# cleaning the table and keeping the top n values
n = 8

  Leiden_coupling_data <- merge(Leiden_coupling[,c("Id","Label", "Titre", "nb_cit")],All_com, by = "Id")
  colnames(Leiden_coupling_data)[colnames(Leiden_coupling_data) == "Community_name_2"] = "Community_name"
  colnames(Leiden_coupling_data)[colnames(Leiden_coupling_data) == "Size_com_2"] = "Size_com"
  Leiden_coupling_data <- Leiden_coupling_data %>% 
    arrange(desc(Resolution),Community_name,desc(nb_cit)) %>%
    group_by(Resolution,Community_name) %>%
    slice(1:n)  %>%
    arrange(desc(Resolution), desc(Size_com), desc(nb_cit))

  # Displaying the table
  datatable(Leiden_coupling_data, rownames = FALSE, 
          options =  list(scrollY = "400px",
  scrollCollapse = TRUE,
  scrollX = "400px",
  paging = FALSE))
  
```


## Sankey diagrams of the links between communities for different resolution

```{r, fig.height= 10, fig.width=15,  eval = TRUE}
# Building the sankey diagrams:
  
# Keeping only the relevant columns and counting the links
sankey_data <- Leiden_coupling[,.SD,.SDcols=c(1,grep("Community_name",colnames(Leiden_coupling)))]
sankey_data <- unique(sankey_data[, value:= .(.N), by = c(colnames(Leiden_coupling[,.SD,.SDcols=grep("Community_name",colnames(Leiden_coupling))]))])[, 2:length(sankey_data)] 

# reogranising in a lode form for plotting
sankey_data <- to_lodes_form(sankey_data,
              axes = 1:length(resolution_set),
              id = "Cohort")

save <- ggplot(sankey_data,
       aes(x = x, stratum = stratum, alluvium = Cohort,
           fill = stratum, label = stratum)) +
  scale_fill_manual(values = c(mypalette,scico(n = 15, palette = "roma"))) +
  geom_flow() +
  geom_stratum() +
  geom_text(stat = "stratum", size = 3) +
  theme(legend.position = "none") +
  ggsave(paste0(picture_path,"Sankey_diagram_Leiden_",start_date[i],"-",end_date[i],".png"), width = 40, height = 30, units = "cm")

include_graphics(path.expand(paste0(picture_path,"Sankey_diagram_Leiden_",start_date[i],"-",end_date[i],".png")))

```


## Sankey diagrams of links between communities for different resolution and cocitation communities