---
title: "test_threshold_for_building_networks"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
##################### Packages, paths, etc. ############################################--------------

source("~/macro_AA/Static_Network_Analysis/functions_for_network_analysis.R")
source("~/macro_AA/Interactive_and_dynamic_networks/Script_paths_and_basic_objects.R")

##################### Loading Data ############################################--------------

nodes_JEL <- readRDS(paste0(data_path,"JEL_matched_corpus_nodes.rds"))
nodes_old_JEL <- readRDS(paste0(data_path,"Old_JEL_matched_corpus_nodes.rds"))
nodes_JEL <- rbind(nodes_JEL,nodes_old_JEL)
rm("nodes_old_JEL")

edges_JEL <- readRDS(paste0(data_path,"JEL_matched_corpus_edges.rds"))
edges_old_JEL <- readRDS(paste0(data_path,"Old_JEL_matched_corpus_edges.rds"))
edges_JEL <- rbind(edges_JEL,edges_old_JEL)
rm("edges_old_JEL")

# Find the time_window
time_window <- 5
all_years <- 1969:1990
```

This document tests different threshold used for building the networks. The issue is twofold:
- finding threshold that are roughly consistent between periods
- avoiding that with the increase of nodes in successive networks, it looks like hairball. 

# Threshold on the number of shared references

This method has the merits of simplicity. Main problem is that with 2, we quickly (around 1980) have network which looks like an hairball. With 3, the first networks with very distanced nodes.

Another thing to test in this section would be the progressive increase of threshold. But the problem is twofold:
- when we increase the threshold of 1, there is a reduction in the size of the network in comparison to the t-1 period, which could lead to weird visualisations.
- the criteria we used for that was a tractability criteria (limiting the number of edges). But the main issue would be the visualisation (avoiding hairball). Not sure we can find an automatic criteria, and we perhaps would have to test the results of such and such thresholds on particular networks.

## edges_threshold = 2

```{r}
tbl_coup_list <- list() 
decile = FALSE

for (Year in all_years) {
  message(paste0("Creation of the network for the ",Year,"-",Year+time_window-1," window."))
  # fixing the initial value of the threshold
  edges_threshold = 2
  
  # creating nodes and edges
  nodes_of_the_year <- nodes_JEL[Annee_Bibliographique>=Year & Annee_Bibliographique<Year+time_window]
  edges_of_the_year <- edges_JEL[ID_Art %in% nodes_of_the_year$ID_Art]
  
  # size of nodes
  nb_cit <- edges_of_the_year[, .N, ItemID_Ref]
  colnames(nb_cit)[colnames(nb_cit) == "N"] <- "size"
  nodes_of_the_year <- merge(nodes_of_the_year, nb_cit, by.x = "ItemID_Ref", by.y = "ItemID_Ref", all.x = TRUE)
  nodes_of_the_year[is.na(size),size:=0]
  
  # coupling
  edges_of_the_year <- bibliographic_coupling(edges_of_the_year, "ID_Art", "New_id2", 
                                              normalized_weight_only = TRUE, weight_threshold = edges_threshold, output_in_character = TRUE)
  
  
  if(decile == TRUE){
    edges_prob_threshold <- quantile(edges_of_the_year$weight, prob = quantile_threshold + 0.0025)
    edges_of_the_year <- edges_of_the_year[weight >= edges_prob_threshold]
  }
  
  # remove nodes with no edges
  nodes_of_the_year <- nodes_of_the_year[ID_Art %in% edges_of_the_year$from | ID_Art %in% edges_of_the_year$to]
  nodes_of_the_year$ID_Art <- as.character(nodes_of_the_year$ID_Art)
  edges_of_the_year$threshold = edges_threshold
  
  # make tbl
  tbl_coup_list[[as.character(Year)]] <- networkflow::tbl_main_component(nodes = nodes_of_the_year, edges = edges_of_the_year, directed = FALSE, node_key = "ID_Art", nb_components = 2)
  
  gc() # cleaning what is not useful anymore
}
```

```{r}
############################# 1.2 Finding Communities ###############################--------
 
tbl_coup_list <- lapply(tbl_coup_list, networkflow::leiden_workflow)

############################ 1.3 Running force atlas #############################--------

list_graph_position <- list()

for (Year in all_years) {
  message(paste0("Running Force Atlas for the ",Year,"-",Year+time_window-1," window."))
  if(is.null(tbl_coup_list[[paste0(Year-1)]])){
    list_graph_position[[paste0(Year)]] <- force_atlas(tbl_coup_list[[paste0(Year)]], kgrav = 4, change_size = FALSE)
  }
  if(!is.null(tbl_coup_list[[paste0(Year-1)]])){
    past_position <- list_graph_position[[paste0(Year-1)]] %>% activate(nodes) %>% as.data.table()
    past_position <- past_position[,.(ID_Art,x,y)]
    tbl <- tbl_coup_list[[paste0(Year)]] %>% activate(nodes) %>% left_join(past_position)
    list_graph_position[[paste0(Year)]] <- force_atlas(tbl, kgrav = 4, change_size = FALSE)
  }
  #saveRDS(tbl_coup_list, paste0(graph_data_path,"coupling_graph_",Year,"-",Year+time_window-1,".rds"))
  saveRDS(list_graph_position[[paste0(Year)]], paste0(graph_data_path,"coupling_graph_",Year,"-",Year+time_window-1,".rds"))
  gc()
}

################################## Integrating Community names (temporary) ############################## 
# Listing all the graph computed in `static_network_analysis.R`
all_nodes <- data.table("Id" = c(), "Annee_Bibliographique" = c(), "Titre" = c(), "Label" = c(), "color" = c(), "Community_name" = c())
for(i in 1:length(start_date)){
  graph <- readRDS(paste0(graph_data_path,"graph_coupling_",start_date[i],"-",end_date[i],".rds"))
  graph <- graph %>% 
    activate(nodes) %>%
    select(Id, Annee_Bibliographique, Titre, Label, color, Community_name) %>%
    as.data.table()
  all_nodes <- rbind(all_nodes, graph)
}

for (Year in all_years) {
  nodes <- list_graph_position[[paste0(Year)]] %>% 
    activate(nodes) %>%
    select(ID_Art, Annee_Bibliographique, Titre, Label, Com_ID) %>%
    as.data.table()
  communities <- all_nodes[between(Annee_Bibliographique,Year, Year + 4)]
  
  communities <- merge(nodes,communities[, c("Id","color","Community_name")], by.x = "ID_Art", by.y = "Id")
  communities <- communities[, size_com := .N, by = "Com_ID"][, .N, by = c("Com_ID","size_com","Community_name","color")]
  
  communities <- communities %>% 
    group_by(Com_ID)  %>% 
    arrange(-N) %>%
    mutate(share = N/size_com) %>%
    select(Com_ID,Community_name,color,share) %>%
    slice(1)
  
  list_graph_position[[paste0(Year)]] <- list_graph_position[[paste0(Year)]] %>%
    activate(nodes) %>%
    left_join(communities)
    
    # Mix color for edges of different color
    list_graph_position[[paste0(Year)]] <- list_graph_position[[paste0(Year)]] %>%
    activate(edges) %>%
    mutate(color_com_ID_to = .N()$color[to], color_com_ID_from = .N()$color[from]) %>%
    mutate(color_edges = DescTools::MixColor(color_com_ID_to, color_com_ID_from, amount1 = 0.5))
  
    # Cleaning progressively
    gc()
}
```

```{r}
################# Projecting graphs #################

com_label <- list()

for (Year in all_years) {
com_label[[paste0(Year)]] <- label_com(list_graph_position[[paste0(Year)]],biggest_community = TRUE, community_threshold = 0.01)
}

list_ggplot <- list()
for (Year in all_years) {
  list_ggplot[[as.character(Year)]] <- ggraph(list_graph_position[[paste0(Year)]], "manual", x = x, y = y) +
    geom_edge_link0(aes(color = color_edges, width = weight), alpha = 0.5) +
    geom_node_point(aes(fill = color, size = size), pch=21) +
    scale_edge_width_continuous(range = c(0.1, 0.5)) +
    scale_size_continuous(range = c(0.1,3)) +
    theme_void() +
   # new_scale("size") +
    geom_label_repel(data=com_label[[paste0(Year)]], aes(x=x, y=y, label = Community_name, fill = color), size = 0.5, fontface="bold", alpha = 0.9, point.padding=NA, show.legend = FALSE) +
    theme(legend.position = "none") +
    scale_fill_identity() +
    scale_edge_colour_identity() +
    labs(title = paste0(as.character(Year),"-",as.character(Year+time_window-1)))
  # ggsave("Networks/coup_2000.png", width=30, height=20, units = "cm")
}


benchmark <- do.call(grid.arrange, list_ggplot[c(1,5,9,13,17,22)])
ggsave(paste0(picture_path,"benchmark_edge_threshold_2.png"), benchmark, width = 30, height = 30, unit = "cm")

```


## edges_threshold = 3

```{r}
tbl_coup_list <- list() 
decile = FALSE
for (Year in all_years) {
  message(paste0("Creation of the network for the ",Year,"-",Year+time_window-1," window."))
  # fixing the initial value of the threshold
  edges_threshold = 3
  
  # creating nodes and edges
  nodes_of_the_year <- nodes_JEL[Annee_Bibliographique>=Year & Annee_Bibliographique<Year+time_window]
  edges_of_the_year <- edges_JEL[ID_Art %in% nodes_of_the_year$ID_Art]
  
  # size of nodes
  nb_cit <- edges_of_the_year[, .N, ItemID_Ref]
  colnames(nb_cit)[colnames(nb_cit) == "N"] <- "size"
  nodes_of_the_year <- merge(nodes_of_the_year, nb_cit, by.x = "ItemID_Ref", by.y = "ItemID_Ref", all.x = TRUE)
  nodes_of_the_year[is.na(size),size:=0]
  
  # coupling
  edges_of_the_year <- bibliographic_coupling(edges_of_the_year, "ID_Art", "New_id2", 
                                              normalized_weight_only = TRUE, weight_threshold = edges_threshold, output_in_character = TRUE)
  
  
  if(decile == TRUE){
    edges_prob_threshold <- quantile(edges_of_the_year$weight, prob = quantile_threshold + 0.0025)
    edges_of_the_year <- edges_of_the_year[weight >= edges_prob_threshold]
  }
  
  # remove nodes with no edges
  nodes_of_the_year <- nodes_of_the_year[ID_Art %in% edges_of_the_year$from | ID_Art %in% edges_of_the_year$to]
  nodes_of_the_year$ID_Art <- as.character(nodes_of_the_year$ID_Art)
  edges_of_the_year$threshold = edges_threshold
  
  # make tbl
  tbl_coup_list[[as.character(Year)]] <- networkflow::tbl_main_component(nodes = nodes_of_the_year, edges = edges_of_the_year, directed = FALSE, node_key = "ID_Art", nb_components = 2)
  
  gc() # cleaning what is not useful anymore
}
```

```{r}
############################# 1.2 Finding Communities ###############################--------
 
tbl_coup_list <- lapply(tbl_coup_list, networkflow::leiden_workflow)

############################ 1.3 Running force atlas #############################--------

list_graph_position <- list()

for (Year in all_years) {
  message(paste0("Running Force Atlas for the ",Year,"-",Year+time_window-1," window."))
  if(is.null(tbl_coup_list[[paste0(Year-1)]])){
    list_graph_position[[paste0(Year)]] <- force_atlas(tbl_coup_list[[paste0(Year)]], kgrav = 4, change_size = FALSE)
  }
  if(!is.null(tbl_coup_list[[paste0(Year-1)]])){
    past_position <- list_graph_position[[paste0(Year-1)]] %>% activate(nodes) %>% as.data.table()
    past_position <- past_position[,.(ID_Art,x,y)]
    tbl <- tbl_coup_list[[paste0(Year)]] %>% activate(nodes) %>% left_join(past_position)
    list_graph_position[[paste0(Year)]] <- force_atlas(tbl, kgrav = 4, change_size = FALSE)
  }
  #saveRDS(tbl_coup_list, paste0(graph_data_path,"coupling_graph_",Year,"-",Year+time_window-1,".rds"))
  saveRDS(list_graph_position[[paste0(Year)]], paste0(graph_data_path,"coupling_graph_",Year,"-",Year+time_window-1,".rds"))
  gc()
}

################################## Integrating Community names (temporary) ############################## 
# Listing all the graph computed in `static_network_analysis.R`
all_nodes <- data.table("Id" = c(), "Annee_Bibliographique" = c(), "Titre" = c(), "Label" = c(), "color" = c(), "Community_name" = c())
for(i in 1:length(start_date)){
  graph <- readRDS(paste0(graph_data_path,"graph_coupling_",start_date[i],"-",end_date[i],".rds"))
  graph <- graph %>% 
    activate(nodes) %>%
    select(Id, Annee_Bibliographique, Titre, Label, color, Community_name) %>%
    as.data.table()
  all_nodes <- rbind(all_nodes, graph)
}

for (Year in all_years) {
  nodes <- list_graph_position[[paste0(Year)]] %>% 
    activate(nodes) %>%
    select(ID_Art, Annee_Bibliographique, Titre, Label, Com_ID) %>%
    as.data.table()
  communities <- all_nodes[between(Annee_Bibliographique,Year, Year + 4)]
  
  communities <- merge(nodes,communities[, c("Id","color","Community_name")], by.x = "ID_Art", by.y = "Id")
  communities <- communities[, size_com := .N, by = "Com_ID"][, .N, by = c("Com_ID","size_com","Community_name","color")]
  
  communities <- communities %>% 
    group_by(Com_ID)  %>% 
    arrange(-N) %>%
    mutate(share = N/size_com) %>%
    select(Com_ID,Community_name,color,share) %>%
    slice(1)
  
  list_graph_position[[paste0(Year)]] <- list_graph_position[[paste0(Year)]] %>%
    activate(nodes) %>%
    left_join(communities)
    
    # Mix color for edges of different color
    list_graph_position[[paste0(Year)]] <- list_graph_position[[paste0(Year)]] %>%
    activate(edges) %>%
    mutate(color_com_ID_to = .N()$color[to], color_com_ID_from = .N()$color[from]) %>%
    mutate(color_edges = DescTools::MixColor(color_com_ID_to, color_com_ID_from, amount1 = 0.5))
  
    # Cleaning progressively
    gc()
}
```

```{r}
################# Projecting graphs #################


com_label <- list()

for (Year in all_years) {
com_label[[paste0(Year)]] <- label_com(list_graph_position[[paste0(Year)]],biggest_community = TRUE, community_threshold = 0.01)
}

list_ggplot <- list()
for (Year in all_years) {
  list_ggplot[[as.character(Year)]] <- ggraph(list_graph_position[[paste0(Year)]], "manual", x = x, y = y) +
    geom_edge_link0(aes(color = color_edges, width = weight), alpha = 0.5) +
    geom_node_point(aes(fill = color, size = size), pch=21) +
    scale_edge_width_continuous(range = c(0.1, 0.5)) +
    scale_size_continuous(range = c(0.1,3)) +
    theme_void() +
   # new_scale("size") +
    geom_label_repel(data=com_label[[paste0(Year)]], aes(x=x, y=y, label = Community_name, fill = color), size = 0.5, fontface="bold", alpha = 0.9, point.padding=NA, show.legend = FALSE) +
    theme(legend.position = "none") +
    scale_fill_identity() +
    scale_edge_colour_identity() +
    labs(title = paste0(as.character(Year),"-",as.character(Year+time_window-1)))
  # ggsave("Networks/coup_2000.png", width=30, height=20, units = "cm")
}


benchmark <- do.call(grid.arrange, list_ggplot[c(1,5,9,13,17,22)])
ggsave(paste0(picture_path,"benchmark_edge_threshold_3.png"), benchmark, width = 30, height = 30, unit = "cm")

```


# Threshold on the distribution of edges weight

The advantage of this method is that it uses the distribution of edges weight: it could clarify the structure of the network rather than acting on the shared references (that is, before the normalisation used by our coupling method). 

The variying quantile method has the advantage of smoothing the increase in networks size (the last decile method also does that a bit), but it is harder to justify changing the quantile progressively.

## Threshold by taking the last decile (the 10% of the nodes with the highest weight value)

```{r}
tbl_coup_list <- list() 
decile = TRUE

for (Year in all_years) {
  message(paste0("Creation of the network for the ",Year,"-",Year+time_window-1," window."))
  # fixing the initial value of the threshold
  edges_threshold = 2
  
  # creating nodes and edges
  nodes_of_the_year <- nodes_JEL[Annee_Bibliographique>=Year & Annee_Bibliographique<Year+time_window]
  edges_of_the_year <- edges_JEL[ID_Art %in% nodes_of_the_year$ID_Art]
  
  # size of nodes
  nb_cit <- edges_of_the_year[, .N, ItemID_Ref]
  colnames(nb_cit)[colnames(nb_cit) == "N"] <- "size"
  nodes_of_the_year <- merge(nodes_of_the_year, nb_cit, by.x = "ItemID_Ref", by.y = "ItemID_Ref", all.x = TRUE)
  nodes_of_the_year[is.na(size),size:=0]
  
  # coupling
  edges_of_the_year <- bibliographic_coupling(edges_of_the_year, "ID_Art", "New_id2", 
                                              normalized_weight_only = TRUE, weight_threshold = edges_threshold, output_in_character = TRUE)
  
  
  if(decile == TRUE){
    edges_prob_threshold <- quantile(edges_of_the_year$weight, prob = 0.9)
    edges_of_the_year <- edges_of_the_year[weight >= edges_prob_threshold]
  }
  
  # remove nodes with no edges
  nodes_of_the_year <- nodes_of_the_year[ID_Art %in% edges_of_the_year$from | ID_Art %in% edges_of_the_year$to]
  nodes_of_the_year$ID_Art <- as.character(nodes_of_the_year$ID_Art)
  edges_of_the_year$threshold = edges_threshold
  
  # make tbl
  tbl_coup_list[[as.character(Year)]] <- networkflow::tbl_main_component(nodes = nodes_of_the_year, edges = edges_of_the_year, directed = FALSE, node_key = "ID_Art", nb_components = 2)
  
  gc() # cleaning what is not useful anymore
}
```

```{r}
############################# 1.2 Finding Communities ###############################--------
 
tbl_coup_list <- lapply(tbl_coup_list, networkflow::leiden_workflow)

############################ 1.3 Running force atlas #############################--------

list_graph_position <- list()

for (Year in all_years) {
  message(paste0("Running Force Atlas for the ",Year,"-",Year+time_window-1," window."))
  if(is.null(tbl_coup_list[[paste0(Year-1)]])){
    list_graph_position[[paste0(Year)]] <- force_atlas(tbl_coup_list[[paste0(Year)]], kgrav = 4, change_size = FALSE)
  }
  if(!is.null(tbl_coup_list[[paste0(Year-1)]])){
    past_position <- list_graph_position[[paste0(Year-1)]] %>% activate(nodes) %>% as.data.table()
    past_position <- past_position[,.(ID_Art,x,y)]
    tbl <- tbl_coup_list[[paste0(Year)]] %>% activate(nodes) %>% left_join(past_position)
    list_graph_position[[paste0(Year)]] <- force_atlas(tbl, kgrav = 4, change_size = FALSE)
  }
  #saveRDS(tbl_coup_list, paste0(graph_data_path,"coupling_graph_",Year,"-",Year+time_window-1,".rds"))
  saveRDS(list_graph_position[[paste0(Year)]], paste0(graph_data_path,"coupling_graph_",Year,"-",Year+time_window-1,".rds"))
  gc()
}

################################## Integrating Community names (temporary) ############################## 
# Listing all the graph computed in `static_network_analysis.R`
all_nodes <- data.table("Id" = c(), "Annee_Bibliographique" = c(), "Titre" = c(), "Label" = c(), "color" = c(), "Community_name" = c())
for(i in 1:length(start_date)){
  graph <- readRDS(paste0(graph_data_path,"graph_coupling_",start_date[i],"-",end_date[i],".rds"))
  graph <- graph %>% 
    activate(nodes) %>%
    select(Id, Annee_Bibliographique, Titre, Label, color, Community_name) %>%
    as.data.table()
  all_nodes <- rbind(all_nodes, graph)
}

for (Year in all_years) {
  nodes <- list_graph_position[[paste0(Year)]] %>% 
    activate(nodes) %>%
    select(ID_Art, Annee_Bibliographique, Titre, Label, Com_ID) %>%
    as.data.table()
  communities <- all_nodes[between(Annee_Bibliographique,Year, Year + 4)]
  
  communities <- merge(nodes,communities[, c("Id","color","Community_name")], by.x = "ID_Art", by.y = "Id")
  communities <- communities[, size_com := .N, by = "Com_ID"][, .N, by = c("Com_ID","size_com","Community_name","color")]
  
  communities <- communities %>% 
    group_by(Com_ID)  %>% 
    arrange(-N) %>%
    mutate(share = N/size_com) %>%
    select(Com_ID,Community_name,color,share) %>%
    slice(1)
  
  list_graph_position[[paste0(Year)]] <- list_graph_position[[paste0(Year)]] %>%
    activate(nodes) %>%
    left_join(communities)
    
    # Mix color for edges of different color
    list_graph_position[[paste0(Year)]] <- list_graph_position[[paste0(Year)]] %>%
    activate(edges) %>%
    mutate(color_com_ID_to = .N()$color[to], color_com_ID_from = .N()$color[from]) %>%
    mutate(color_edges = DescTools::MixColor(color_com_ID_to, color_com_ID_from, amount1 = 0.5))
  
    # Cleaning progressively
    gc()
}
```

```{r}
################# Projecting graphs #################

com_label <- list()

for (Year in all_years) {
com_label[[paste0(Year)]] <- label_com(list_graph_position[[paste0(Year)]],biggest_community = TRUE, community_threshold = 0.01)
}

list_ggplot <- list()
for (Year in all_years) {
  list_ggplot[[as.character(Year)]] <- ggraph(list_graph_position[[paste0(Year)]], "manual", x = x, y = y) +
    geom_edge_link0(aes(color = color_edges, width = weight), alpha = 0.5) +
    geom_node_point(aes(fill = color, size = size), pch=21) +
    scale_edge_width_continuous(range = c(0.1, 0.5)) +
    scale_size_continuous(range = c(0.1,3)) +
    theme_void() +
   # new_scale("size") +
    geom_label_repel(data=com_label[[paste0(Year)]], aes(x=x, y=y, label = Community_name, fill = color), size = 0.5, fontface="bold", alpha = 0.9, point.padding=NA, show.legend = FALSE) +
    theme(legend.position = "none") +
    scale_fill_identity() +
    scale_edge_colour_identity() +
    labs(title = paste0(as.character(Year),"-",as.character(Year+time_window-1)))
  # ggsave("Networks/coup_2000.png", width=30, height=20, units = "cm")
}


benchmark <- do.call(grid.arrange, list_ggplot[c(1,5,9,13,17,22)])
ggsave(paste0(picture_path,"benchmark_weight_threshold_0.9.png"), benchmark, width = 30, height = 30, unit = "cm")

```


## Threshold with a varying quantile threshold (the 20% highest weight values, with a 0,25% decreasing for each year)

```{r}
tbl_coup_list <- list() 
decile = TRUE
quantile_threshold = 0.8

for (Year in all_years) {
  message(paste0("Creation of the network for the ",Year,"-",Year+time_window-1," window."))
  # fixing the initial value of the threshold
  edges_threshold = 1
  
  # creating nodes and edges
  nodes_of_the_year <- nodes_JEL[Annee_Bibliographique>=Year & Annee_Bibliographique<Year+time_window]
  edges_of_the_year <- edges_JEL[ID_Art %in% nodes_of_the_year$ID_Art]
  
  # size of nodes
  nb_cit <- edges_of_the_year[, .N, ItemID_Ref]
  colnames(nb_cit)[colnames(nb_cit) == "N"] <- "size"
  nodes_of_the_year <- merge(nodes_of_the_year, nb_cit, by.x = "ItemID_Ref", by.y = "ItemID_Ref", all.x = TRUE)
  nodes_of_the_year[is.na(size),size:=0]
  
  # coupling
  edges_of_the_year <- bibliographic_coupling(edges_of_the_year, "ID_Art", "New_id2", 
                                              normalized_weight_only = TRUE, weight_threshold = edges_threshold, output_in_character = TRUE)
  
  
  if(decile == TRUE){
    edges_prob_threshold <- quantile(edges_of_the_year$weight, prob = quantile_threshold + 0.0025)
    edges_of_the_year <- edges_of_the_year[weight >= edges_prob_threshold]
  }
  
  message(paste0("The final threshold for edges is:",edges_threshold))
  # remove nodes with no edges
  nodes_of_the_year <- nodes_of_the_year[ID_Art %in% edges_of_the_year$from | ID_Art %in% edges_of_the_year$to]
  nodes_of_the_year$ID_Art <- as.character(nodes_of_the_year$ID_Art)
  edges_of_the_year$threshold = edges_threshold
  
  # make tbl
  tbl_coup_list[[as.character(Year)]] <- networkflow::tbl_main_component(nodes = nodes_of_the_year, edges = edges_of_the_year, directed = FALSE, node_key = "ID_Art", nb_components = 2)
  
  gc() # cleaning what is not useful anymore
}

```

```{r}
############################# 1.2 Finding Communities ###############################--------
 
tbl_coup_list <- lapply(tbl_coup_list, networkflow::leiden_workflow)

############################ 1.3 Running force atlas #############################--------

list_graph_position <- list()

for (Year in all_years) {
  message(paste0("Running Force Atlas for the ",Year,"-",Year+time_window-1," window."))
  if(is.null(tbl_coup_list[[paste0(Year-1)]])){
    list_graph_position[[paste0(Year)]] <- force_atlas(tbl_coup_list[[paste0(Year)]], kgrav = 4, change_size = FALSE)
  }
  if(!is.null(tbl_coup_list[[paste0(Year-1)]])){
    past_position <- list_graph_position[[paste0(Year-1)]] %>% activate(nodes) %>% as.data.table()
    past_position <- past_position[,.(ID_Art,x,y)]
    tbl <- tbl_coup_list[[paste0(Year)]] %>% activate(nodes) %>% left_join(past_position)
    list_graph_position[[paste0(Year)]] <- force_atlas(tbl, kgrav = 4, change_size = FALSE)
  }
  #saveRDS(tbl_coup_list, paste0(graph_data_path,"coupling_graph_",Year,"-",Year+time_window-1,".rds"))
  saveRDS(list_graph_position[[paste0(Year)]], paste0(graph_data_path,"coupling_graph_",Year,"-",Year+time_window-1,".rds"))
  gc()
}

################################## Integrating Community names (temporary) ############################## 
# Listing all the graph computed in `static_network_analysis.R`
all_nodes <- data.table("Id" = c(), "Annee_Bibliographique" = c(), "Titre" = c(), "Label" = c(), "color" = c(), "Community_name" = c())
for(i in 1:length(start_date)){
  graph <- readRDS(paste0(graph_data_path,"graph_coupling_",start_date[i],"-",end_date[i],".rds"))
  graph <- graph %>% 
    activate(nodes) %>%
    select(Id, Annee_Bibliographique, Titre, Label, color, Community_name) %>%
    as.data.table()
  all_nodes <- rbind(all_nodes, graph)
}

for (Year in all_years) {
  nodes <- list_graph_position[[paste0(Year)]] %>% 
    activate(nodes) %>%
    select(ID_Art, Annee_Bibliographique, Titre, Label, Com_ID) %>%
    as.data.table()
  communities <- all_nodes[between(Annee_Bibliographique,Year, Year + 4)]
  
  communities <- merge(nodes,communities[, c("Id","color","Community_name")], by.x = "ID_Art", by.y = "Id")
  communities <- communities[, size_com := .N, by = "Com_ID"][, .N, by = c("Com_ID","size_com","Community_name","color")]
  
  communities <- communities %>% 
    group_by(Com_ID)  %>% 
    arrange(-N) %>%
    mutate(share = N/size_com) %>%
    select(Com_ID,Community_name,color,share) %>%
    slice(1)
  
  list_graph_position[[paste0(Year)]] <- list_graph_position[[paste0(Year)]] %>%
    activate(nodes) %>%
    left_join(communities)
    
    # Mix color for edges of different color
    list_graph_position[[paste0(Year)]] <- list_graph_position[[paste0(Year)]] %>%
    activate(edges) %>%
    mutate(color_com_ID_to = .N()$color[to], color_com_ID_from = .N()$color[from]) %>%
    mutate(color_edges = DescTools::MixColor(color_com_ID_to, color_com_ID_from, amount1 = 0.5))
  
    # Cleaning progressively
    gc()
}
```

```{r}
################# Projecting graphs #################


com_label <- list()

for (Year in all_years) {
com_label[[paste0(Year)]] <- label_com(list_graph_position[[paste0(Year)]],biggest_community = TRUE, community_threshold = 0.01)
}

list_ggplot <- list()
for (Year in all_years) {
  list_ggplot[[as.character(Year)]] <- ggraph(list_graph_position[[paste0(Year)]], "manual", x = x, y = y) +
    geom_edge_link0(aes(color = color_edges, width = weight), alpha = 0.5) +
    geom_node_point(aes(fill = color, size = size), pch=21) +
    scale_edge_width_continuous(range = c(0.1, 0.5)) +
    scale_size_continuous(range = c(0.1,3)) +
    theme_void() +
   # new_scale("size") +
    geom_label_repel(data=com_label[[paste0(Year)]], aes(x=x, y=y, label = Community_name, fill = color), size = 0.5, fontface="bold", alpha = 0.9, point.padding=NA, show.legend = FALSE) +
    theme(legend.position = "none") +
    scale_fill_identity() +
    scale_edge_colour_identity() +
    labs(title = paste0(as.character(Year),"-",as.character(Year+time_window-1)))
  # ggsave("Networks/coup_2000.png", width=30, height=20, units = "cm")
}


benchmark <- do.call(grid.arrange, list_ggplot[c(1,5,9,13,17,22)])
ggsave(paste0(picture_path,"benchmark_weight_varying_threshold.png"), benchmark, width = 30, height = 30, unit = "cm")

```
